analyze_growth

### 2024-09-26 smelt_2019_allseasons/analyze_growth.Rmd
Saved new figure files with requested colors and legend labels. Saved plots within Rdata.

  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
     geom_text( aes(label = .group, x = Season, y = upper.CL + 0.01), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
     annotate(geom = "text", x = 3.2, y = 0.1, label = "B", size = 8) +
  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
  viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
  labs(y = "Proportional Change in K \nwith 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        axis.text.y = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
   geom_text( aes(label = .group, x = Season, y = upper.CL + 0.02), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
     annotate(geom = "text", x = 3.2, y = 0.24, label = "A", size = 8) +
    viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
  labs(y = "Proportional Change in Weight \nwith 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

# plots ----------
library(patchwork)
png(filename = "smelt_2019_allseasons/figures/RV_weight_k_season.png", height = 5, width = 9,units = "in", 
    res = 300, pointsize = 12, family = "sans")
plot_season_wt & plot_season_k
dev.off()
```

@@

  geom_segment(aes(x = Site, y = emmean, xend = Site, yend = rcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
    geom_segment(aes(x = Site, y = emmean, xend = Site, yend = lcmpl, color = .group), size = 6, color = "cadetblue3", lineend = "butt") +
      geom_errorbar(aes(x = Site, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
    geom_text( aes(label = .group, x = Site, y = upper.CL + 0.01), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
        annotate(geom = "text", x = 4.1, y = -0.005, label = "D", size =8) +
  geom_point( aes(x=Site, y=emmean), size = 2.5, shape = 18) +     
  viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
  labs(y = "Proportional Change in K \nwith 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        axis.text.y = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

# plots ----------
library(patchwork)
png(filename = "smelt_2019_allseasons/figures/model_fall_site.png", height = 5, width = 9,units = "in", 
    res = 300, pointsize = 12, family = "sans")
plot_Site_wt & plot_Site_k
dev.off()
```

>>>>

  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
     geom_text( aes(label = .group, x = Season, y = upper.CL + 0.01), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
     annotate(geom = "text", x = 3.2, y = 0.1, label = "A", size = 8) +
  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
  viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
  labs(y = "Proportional Change in K \nwith 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        axis.text.y = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

  geom_segment(aes(x = Season, y = emmean, xend = Season, yend = rcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
    geom_segment(aes(x = Season, y = emmean, xend = Season, yend = lcmpl, color = .group), size = 6, color = "#0072B2", lineend = "butt") +
  geom_point( aes(x=Season, y=emmean), size = 2.5, shape = 18) +     
   geom_text( aes(label = .group, x = Season, y = upper.CL + 0.02), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
     annotate(geom = "text", x = 3.2, y = 0.24, label = "A", size = 8) +
    viridis::scale_color_viridis(discrete = TRUE, option = "turbo") +
  labs(y = "Proportional Change in Weight \nwith 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

# plots ----------
library(patchwork)
png(filename = "smelt_2019_allseasons/figures/RV_weight_k_season.png", height = 5, width = 9,units = "in", 
    res = 300, pointsize = 12, family = "sans")
plot_season_wt & plot_season_k
dev.off()

png(filename = "smelt_2019_allseasons/figures/RV_k_season.png", height = 4, width = 5,units = "in", 
    res = 300, pointsize = 12, family = "sans")
plot_season_k
dev.off()
```

@@

  geom_segment(aes(x = Site, y = emmean, xend = Site, yend = rcmpl, color = Site), size = 6,  lineend = "butt") +
    geom_segment(aes(x = Site, y = emmean, xend = Site, yend = lcmpl, color = Site), size = 6,  lineend = "butt") +
      geom_errorbar(aes(x = Site, ymin = lower.CL, ymax = upper.CL), size = 0.5,  width = 0.1) +
    geom_text( aes(label = .group, x = Site, y = upper.CL + 0.01), position = position_dodge2(width = 0.3)) + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
        annotate(geom = "text", x = 4.1, y = -0.005, label = "B", size =8) +
  geom_point( aes(x=Site, y=emmean), size = 2.5, shape = 18) +     
  scale_color_manual(values=c("#E69F00", "#0072B2", "#009E73","#D55E00"))  +
  labs(y = "Proportional Change in K \nwith 95% Confidence Intervals") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        axis.text.y = element_text(size = 11),
        legend.position = "top",
        axis.title.x = element_blank()) )
```

@@

# plots ----------
library(patchwork)
png(filename = "smelt_2019_allseasons/figures/model_fall_site.png", height = 5, width = 9,units = "in", 
    res = 300, pointsize = 12, family = "sans")
plot_Site_wt & plot_Site_k
dev.off()

png(filename = "smelt_2019_allseasons/figures/model_fall_site_k.png", height = 4, width = 5,units = "in", 
    res = 300, pointsize = 12, family = "sans")
 plot_Site_k
dev.off()

# plots in Rdata for Britt -------
save(plot_Site_k, plot_season_k, file = "smelt_2019_allseasons/figures/updated_k_plots.Rdata")

load("smelt_2019_allseasons/figures/updated_k_plots.Rdata")
```
